\bf A Comparision of Bootstrap Confidence Interval Methods

### 2022-12-06 project/PaperTemplate/paper.tex
Redid simulation

\if0\blind
{
  \title{\bf A Comparision of Bootstrap Methods}

@@

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf A Comparision of Bootstrap Methods}
  \end{center}
  \medskip
} \fi

@@

\noindent%
{\it Keywords:} confidence
interval, simulation, percentile, bias-corrected, acceleration, studentized
\vfill

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{orig\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\CommentTok{\# theta hat}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_dhistogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\AttributeTok{data =}\NormalTok{ dec\_means) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{gf\_dens}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{gf\_labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Histogram of 10,000 Bootstrapped Mean Dec Values"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.85639}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.65957}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91170}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.72353}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{14.01172}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.82017}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in Decemeber"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in Decemeber"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91591}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.72353}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

@@

Third, we sample from a Log-Normal distribution with mean log of 0 and a
mean standard deviation of 1. Therefore, the true population mean of
this distribution is \(e^{\frac{1}{2}}\) \citep{Guillaume21}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{run\_simulation\_log\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(simulation\_rep)\{}
\NormalTok{  trueparameter }\OtherTok{\textless{}{-}} \FunctionTok{exp}\NormalTok{(}\DecValTok{1}\SpecialCharTok{/}\DecValTok{2}\NormalTok{)}

\NormalTok{  X }\OtherTok{\textless{}{-}} \FunctionTok{rlnorm}\NormalTok{(sample\_sizes, }\AttributeTok{meanlog =} \DecValTok{0}\NormalTok{, }\AttributeTok{sdlog =} \DecValTok{1}\NormalTok{)}
\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{findCIs}\NormalTok{(values, }\DecValTok{2000}\NormalTok{)}
\NormalTok{  ci }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\FunctionTok{c}\NormalTok{(trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{]), }\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)}
\NormalTok{  res }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(), ci)}
\NormalTok{  res}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

Lastly, we sample from a Beta distribution with shape parameters of 4
and 1 which gives us a true population mean of 0.8.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{run\_simulation\_beta }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(simulation\_rep)\{}
\NormalTok{  trueparameter }\OtherTok{\textless{}{-}} \FloatTok{0.8}

\NormalTok{  X }\OtherTok{\textless{}{-}} \FunctionTok{rbeta}\NormalTok{(sample\_sizes, }\AttributeTok{shape1 =} \DecValTok{4}\NormalTok{, }\AttributeTok{shape2 =} \DecValTok{1}\NormalTok{)}
\NormalTok{  values }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(X)}
\NormalTok{  output }\OtherTok{\textless{}{-}} \FunctionTok{findCIs}\NormalTok{(values, }\DecValTok{2000}\NormalTok{)}
\NormalTok{  ci }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\FunctionTok{c}\NormalTok{(trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Standard Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Percentile Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&}
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BC Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{BCa Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{],}
\NormalTok{    trueparameter }\SpecialCharTok{\textgreater{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{1}\NormalTok{] }\SpecialCharTok{\&} 
\NormalTok{    trueparameter }\SpecialCharTok{\textless{}=}\NormalTok{ output}\SpecialCharTok{$}\StringTok{\textasciigrave{}}\AttributeTok{Studentized Interval}\StringTok{\textasciigrave{}}\NormalTok{[}\DecValTok{2}\NormalTok{]), }\AttributeTok{nrow =} \DecValTok{1}\NormalTok{)}
\NormalTok{  res }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(}\FunctionTok{data.frame}\NormalTok{(), ci)}
\NormalTok{  res}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{collect\_data\_gamma }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{50}
  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
\NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_gamma, }\AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
\NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps)}

\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{*}\DecValTok{2}
\NormalTok{  \}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{collect\_data\_log\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{50}

  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
\NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_log\_normal, }\AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
\NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{unname}\NormalTok{(}\FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps)}

\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{*}\DecValTok{2}
\NormalTok{  \}}

\NormalTok{  log\_normal\_output }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(data2) }\SpecialCharTok{\%\textgreater{}\%} 
    \FunctionTok{rename}\NormalTok{(}\StringTok{"Sample\_Size"} \OtherTok{=}\NormalTok{ V1, }\StringTok{"Standard"} \OtherTok{=}\NormalTok{ V2, }\StringTok{"Percentile"} \OtherTok{=}\NormalTok{ V3, }\StringTok{"BC"} \OtherTok{=}\NormalTok{ V4, }
           \StringTok{"BCa"} \OtherTok{=}\NormalTok{ V5, }\StringTok{"Studentized"} \OtherTok{=}\NormalTok{ V6) }
\NormalTok{  log\_normal\_output}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{collect\_data\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{50}

@@

\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{*}\DecValTok{2}
\NormalTok{  \}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{collect\_data\_beta }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{50}

>>>>

\if0\blind
{
  \title{\bf A Comparision of Bootstrap Confidence Interval Methods}

@@

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf A Comparision of Bootstrap Confidence Interval Methods}
  \end{center}
  \medskip
} \fi

@@

\noindent%
{\it Keywords:} simulation, percentile, bias-corrected, acceleration, studentized
\vfill

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 1: Histogram with Studentized Interval Shown"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
\NormalTok{orig\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\CommentTok{\# theta hat}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_dhistogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ mean, }\AttributeTok{data =}\NormalTok{ dec\_means) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{gf\_dens}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{gf\_labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Histogram of 10,000 Bootstrapped Mean Dec Values"}\NormalTok{,}
          \AttributeTok{caption =} \StringTok{"Fig. 2: Bootstrap Histogram"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 3: Histogram with Standard Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.85639}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.65957}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 4: Histogram with Percentile Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91170}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.72353}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 5: Histogram with BC Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{14.01172}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.82017}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 6: Histogram with BCa Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91591}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.72353}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

This would give us the following histogram:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{, }
       \AttributeTok{caption =} \StringTok{"Fig. 7: Histogram with Studentized Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{14.03467}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{18.01709}\NormalTok{)) }
\end{Highlighting}
\end{Shaded}

\includegraphics{paper_files/figure-latex/unnamed-chunk-19-1.pdf}

@@

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{collect\_data\_gamma }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{10}

  \ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{) \{}
\NormalTok{    simulation\_rep }\OtherTok{\textless{}{-}} \FunctionTok{seq}\NormalTok{(}\DecValTok{1}\NormalTok{,sim\_reps)}
\NormalTok{    results }\OtherTok{\textless{}{-}} \FunctionTok{mclapply}\NormalTok{(simulation\_rep, run\_simulation\_gamma, }
                        \AttributeTok{mc.cores =} \FunctionTok{detectCores}\NormalTok{())}
\NormalTok{    df }\OtherTok{\textless{}{-}} \FunctionTok{data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\FunctionTok{unlist}\NormalTok{(results), }\AttributeTok{nrow=}\FunctionTok{length}\NormalTok{(results), }\AttributeTok{byrow=}\ConstantTok{TRUE}\NormalTok{))}
\NormalTok{    ci\_prop }\OtherTok{\textless{}{-}} \FunctionTok{colSums}\NormalTok{(df)}\SpecialCharTok{/}\NormalTok{sim\_reps}

\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{+}\DecValTok{10}
\NormalTok{  \}}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{collect\_data\_normal }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(sim\_reps) \{}
\NormalTok{  data2 }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\AttributeTok{nrow =} \DecValTok{5}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{6}\NormalTok{)}
\NormalTok{  sample\_sizes }\OtherTok{=} \DecValTok{10}

@@

\NormalTok{    data2[i, }\DecValTok{1}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}
\NormalTok{    data2[i, }\DecValTok{2}\SpecialCharTok{:}\DecValTok{6}\NormalTok{] }\OtherTok{\textless{}{-}}\NormalTok{ ci\_prop}
\NormalTok{    sample\_sizes }\OtherTok{\textless{}{-}}\NormalTok{ sample\_sizes}\SpecialCharTok{+}\DecValTok{10}
\NormalTok{  \}}

@@
